Unknown

### 2024-03-07 ms/ms.qmd
methods and outlining predictions

# I am mostly putting placeholders here for objects/values that will need to be
# loaded eventually to use in paper.
n_plant = 600
n_acc = 30
mean_n_rep = 10 # average number of individual replicates for accession per light treatment

@@

@@

|  hypothesis  | native light habitat | light treatment  | light intensity |
|:------------:|:--------------------:|:----------------:|:---------------:|
| acclimatory  |   cor(PAR, AA) = 0   | AAsun = AAshade  | AA2000 \> AA150 |
|   plastic    | cor(PAR, AAsun) \> 0 | AAsun \> AAshade | AA2000 = AA150  |
| constitutive |  cor(PAR, AA) \> 0   | AAsun = AAshade  | AA2000 = AA150  |

@@

#### Internal leaf anatomy

Add information on internal leaf anatomy, if using

@@

>>>>

library(readr)
# I am mostly putting placeholders here for objects/values that will need to be
# loaded eventually to use in paper.
fit_aa = read_rds("../objects/fit_dummy.rds")
dim_fit_aa = dim(fit_aa$fit)

n_plant = 600
n_acc = 30
mean_n_rep = 10 # average number of individual replicates for accession per light treatment

@@

## Authors

definite: Wei Shen Lim, Dachuan Wang, Chris Muir
question: Sam McKlin, Tom Buckley

@@

|  hypothesis  | native light habitat | light treatment  | light intensity |
|:------------:|:--------------------:|:----------------:|:---------------:|
| acclimatory  | cor(PAR, AA) = 0   | AAsun = AAshade  | AA2000 \> AA150 |
|   plastic    | cor(PAR, AA) = 0 | AAsun \> AAshade | AA2000 = AA150  |
| constitutive | cor(PAR, AA) \> 0   | AAsun = AAshade  | AA2000 = AA150  |

@@

<!-- 
#### Internal leaf anatomy

Add information on internal leaf anatomy, if using 
-->

@@

### Data analysis

#### General points (not sure where this goes yet)

- models fit in Stan/brms
- warmup and sampling iterations were chosen so that parameter ESS > 1000 and  $\hat{R} < 1.01$ [@gelman_inference_1992] and the effective sample size (ESS) was greater than $10^3$.

We fit Bayesian models using the *R* package **brms** version `r fit_aa$version$brms` [@burkner_brms_2017] with MCMC sampling in *Stan* [@stan_development_team_stan_2023]. We used CmdStan version `r fit_aa$version$cmdstan` and **cmdstanr** version `r fit_aa$version$cmdstanr` [@gabry_cmdstanr_2023] to interface with *R* version `r getRversion()` [@r_core_team_r:_2023]. We sampled the posterior distribution from `r dim_fit_aa[2]` chains with `r dim_fit_aa[1]` iterations each after `r dim_fit_aa[1]` warmup iterations per chain. We estimated parameters and confidence intervals as the median and 95% quantile intervals of the posterior, respectively.

#### Parameter estimates (this is a provisional section)

* Assimilatory: 
  + average AA2000 - AA150
  + among accession variation in AA2000 - AA150
* Plastic
  + average AAsun - AAshade
  + among accession variation in AAsun - AAshade
* Constitutive
  + cor(PAR, AA) at accession level

Reinforcing interactions (we only consider these because these are ones which could explain why amphi leaves occur in high light habitats)

* Assimilatory * Plastic (reinforcing interaction)
  + AAsun - AAshade greater at 2000 than 150
  + AA2000 - AA150 greater in sun leaves than shade leaves
  + there may be var among accessions, but not correlated with PAR

* Assimilatory * Constitutive (reinforcing interaction)
  + cor(AA2000, PAR) > 0; cor(AA150, PAR) = 0
  + AA2000 - AA150 varies among accessions, correlated with PAR

* Plastic * Constitutive (reinforcing interaction)
  + cor(AAsun, PAR) > 0; cor(AAshade, PAR) = 0
  + AAsun - AAshade varies among accessions, correlated with PAR

* Assimilatory * Plastic * Constitutive (reinforcing interaction)
  + AAsun - AAshade greater at 2000 than 150
  + AA2000 - AA150 greater in sun leaves than shade leaves
  + AAsun - AAshade varies among accession, correlated with PAR
  + AA2000 - AA150 varies among accession, correlated with PAR
  + cor(AAsun2000, PAR) > cor(AAsun150, PAR) and > cor(AAshade2000, PAR) and > cor(AAshade150, PAR) in nonadditive way
## Acknowledgements

Justin Alter, Max Gatlin, Joana Kim, Jenna Matsuyama, Brandon Najarian, Kai Yasuda

### 2024-03-07 ms/ms.tex
methods and outlining predictions

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\KOMAoption{captions}{tableheading}
\addtokomafont{disposition}{\rmfamily}
\usepackage{siunitx}
\newcommand{\aax}{$\mathrm{AA}$}
\newcommand{\Aamphi}{$A_{\mathrm{amphi}}$}
\newcommand{\Ahypo}{$A_{\mathrm{hypo}}$}
\newcommand{\agcurve}{$A \textendash g_\text{sw}$}
\newcommand{\caequals}[1]{$C_\mathrm{a} = \qty{#1}{\micro\mol\raiseto{-1}\mol}$}
\newcommand{\gsw}{$g_\text{sw}$}
\newcommand{\ppfd}{$\mathrm{PPFD}$}
\newcommand{\ppfdequals}[1]{$\mathrm{PPFD} = \qty{#1}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}$}
\newcommand{\rh}{$\mathrm{RH}$}
\newcommand{\rhequals}[1]{$\mathrm{RH} = #1\%$}
\newcommand{\tleafequals}[1]{$T_\mathrm{leaf} = \qty{#1}{\degreeCelsius}$}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Unknown},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{document}
\maketitle

\subsection{Notes}\label{notes}

@@

\subsection{Main}\label{main}

@@

\subsection{Materials and Methods}\label{materials-and-methods}

@@

\subsubsection{Accessions}\label{accessions}

@@

\caption{\label{tbl-accessions}Solanum accessions}

\centering{

}

\end{table}%

\subsubsection{Plant growth conditions}\label{plant-growth-conditions}

@@

\paragraph{Germination and seedling
stage}\label{germination-and-seedling-stage}

@@

\paragraph{Light treatments}\label{light-treatments}

@@

\subsubsection{Leaf trait measurements}\label{leaf-trait-measurements}

@@

\paragraph{Amphistomy advantage}\label{amphistomy-advantage}

@@

\paragraph{Light-response curves}\label{light-response-curves}

@@

\paragraph{Stomatal anatomy}\label{stomatal-anatomy}

@@

\paragraph{Internal leaf anatomy}\label{internal-leaf-anatomy}

Add information on internal leaf anatomy, if using

\paragraph{Leaf mass per area}\label{leaf-mass-per-area}

@@

\subsection*{References}\label{references}
\addcontentsline{toc}{subsection}{References}

\phantomsection\label{refs}
\begin{CSLReferences}{0}{1}
\bibitem[\citeproctext]{ref-triplett_amphistomy_2024}
\CSLLeftMargin{1. }%
\CSLRightInline{G. Triplett, T. N. Buckley, C. D. Muir,
\href{https://doi.org/10.1002/ajb2.16284}{Amphistomy increases leaf
photosynthesis more in coastal than montane plants of {Hawaiian} ʻilima
( \emph{{Sida} fallax} )}. \emph{American Journal of Botany}
\textbf{111}, e16284 (2024).}

\bibitem[\citeproctext]{ref-peralta_taxonomy_2008}
\CSLLeftMargin{2. }%
\CSLRightInline{I. E. Peralta, D. M. Spooner, S. Knapp, Taxonomy of wild
tomatoes and their relatives (\emph{solanum} sect.
\emph{Lycopersicoides}, sect. \emph{Juglandifolia}, sect.
\emph{Lycopersicon}; {Solanaceae}). \textbf{84} (2008).}

\bibitem[\citeproctext]{ref-schoch_dependence_1980}
\CSLLeftMargin{3. }%
\CSLRightInline{P.-G. Schoch, C. Zinsou, M. Sibi,
\href{https://doi.org/10.1093/jxb/31.5.1211}{Dependence of the stomatal
index on environmental factors during stomatal differentiation in leaves
of \emph{{Vigna} sinensis} {L}.: 1. {Effect} of light intensity}.
\emph{Journal of Experimental Botany} \textbf{31}, 1211--1216 (1980).}

\bibitem[\citeproctext]{ref-parkhurst_adaptive_1978}
\CSLLeftMargin{4. }%
\CSLRightInline{D. F. Parkhurst,
\href{https://doi.org/10.2307/2259142}{The adaptive significance of
stomatal occurrence on one or both surfaces of leaves}. \emph{The
Journal of Ecology} \textbf{66}, 367--383 (1978).}

\bibitem[\citeproctext]{ref-sack_developmental_2016}
\CSLLeftMargin{5. }%
\CSLRightInline{L. Sack, T. N. Buckley,
\href{https://doi.org/10.1104/pp.16.00476}{The developmental basis of
stomatal density and flux}. \emph{Plant Physiology} \textbf{171},
2358--2363 (2016).}

\bibitem[\citeproctext]{ref-mott_amphistomy_1991}
\CSLLeftMargin{6. }%
\CSLRightInline{K. A. Mott, O. Michaelson, Amphistomy as an adaptation
to high light intensity in \emph{{Ambrosia} cordifolia} ({Compositae}).
\emph{American Journal of Botany} \textbf{78}, 76--79 (1991).}

\bibitem[\citeproctext]{ref-schindelin_fiji_2012}
\CSLLeftMargin{7. }%
\CSLRightInline{J. Schindelin, I. Arganda-Carreras, E. Frise, V. Kaynig,
M. Longair, T. Pietzsch, S. Preibisch, C. Rueden, S. Saalfeld, B.
Schmid, J.-Y. Tinevez, D. J. White, V. Hartenstein, K. Eliceiri, P.
Tomancak, A. Cardona, \href{https://doi.org/10.1038/nmeth.2019}{Fiji: An
open-source platform for biological-image analysis}. \emph{Nature
Methods} \textbf{9}, 676--682 (2012).}

>>>>

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\KOMAoption{captions}{tableheading}
\addtokomafont{disposition}{\rmfamily}
\usepackage{siunitx}
\newcommand{\aax}{$\mathrm{AA}$}
\newcommand{\Aamphi}{$A_{\mathrm{amphi}}$}
\newcommand{\Ahypo}{$A_{\mathrm{hypo}}$}
\newcommand{\agcurve}{$A \textendash g_\text{sw}$}
\newcommand{\caequals}[1]{$C_\mathrm{a} = \qty{#1}{\micro\mol\raiseto{-1}\mol}$}
\newcommand{\gsw}{$g_\text{sw}$}
\newcommand{\ppfd}{$\mathrm{PPFD}$}
\newcommand{\ppfdequals}[1]{$\mathrm{PPFD} = \qty{#1}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}$}
\newcommand{\rh}{$\mathrm{RH}$}
\newcommand{\rhequals}[1]{$\mathrm{RH} = #1\%$}
\newcommand{\tleafequals}[1]{$T_\mathrm{leaf} = \qty{#1}{\degreeCelsius}$}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Unknown},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, interior hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, sharp corners, frame hidden, enhanced]}{\end{tcolorbox}}\fi

\hypertarget{notes}{%
\subsection{Notes}\label{notes}}

@@

\hypertarget{main}{%
\subsection{Main}\label{main}}

@@

\hypertarget{materials-and-methods}{%
\subsection{Materials and Methods}\label{materials-and-methods}}

@@

\hypertarget{accessions}{%
\subsubsection{Accessions}\label{accessions}}

@@

\end{table}

\hypertarget{plant-growth-conditions}{%
\subsubsection{Plant growth conditions}\label{plant-growth-conditions}}

@@

\hypertarget{germination-and-seedling-stage}{%
\paragraph{Germination and seedling
stage}\label{germination-and-seedling-stage}}

@@

\hypertarget{light-treatments}{%
\paragraph{Light treatments}\label{light-treatments}}

@@

\hypertarget{leaf-trait-measurements}{%
\subsubsection{Leaf trait measurements}\label{leaf-trait-measurements}}

@@

\hypertarget{amphistomy-advantage}{%
\paragraph{Amphistomy advantage}\label{amphistomy-advantage}}

@@

\hypertarget{light-response-curves}{%
\paragraph{Light-response curves}\label{light-response-curves}}

@@

\hypertarget{stomatal-anatomy}{%
\paragraph{Stomatal anatomy}\label{stomatal-anatomy}}

@@

\hypertarget{leaf-mass-per-area}{%
\paragraph{Leaf mass per area}\label{leaf-mass-per-area}}

@@

\hypertarget{data-analysis}{%
\subsubsection{Data analysis}\label{data-analysis}}

\hypertarget{general-points-not-sure-where-this-goes-yet}{%
\paragraph{General points (not sure where this goes
yet)}\label{general-points-not-sure-where-this-goes-yet}}

\begin{itemize}
\tightlist
\item
  models fit in Stan/brms
\item
  warmup and sampling iterations were chosen so that parameter ESS
  \textgreater{} 1000 and \(\hat{R} < 1.01\) (\emph{8}) and the
  effective sample size (ESS) was greater than \(10^3\).
\end{itemize}

We fit Bayesian models using the \emph{R} package \textbf{brms} version
2.20.4 (\emph{9}) with MCMC sampling in \emph{Stan} version XXX
(\emph{10}). We used CmdStan version 2.33.1 and \textbf{cmdstanr}
version 0.7.1 (\emph{11}) to interface with \emph{R} version 4.3.2
(\emph{12}). We sampled the posterior distribution from 4 chains with
1000 iterations each after 1000 warmup iterations per chain. We
estimated parameters and confidence intervals as the median and 95\%
quantile intervals of the posterior, respectively.

\hypertarget{references}{%
\subsection*{References}\label{references}}
\addcontentsline{toc}{subsection}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\leavevmode\vadjust pre{\hypertarget{ref-triplett_amphistomy_2024}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{G. Triplett, T. N. Buckley, C. D. Muir,
\href{https://doi.org/10.1002/ajb2.16284}{Amphistomy increases leaf
photosynthesis more in coastal than montane plants of {Hawaiian} ʻilima
( \emph{{Sida} fallax} )}. \emph{American Journal of Botany}
\textbf{111}, e16284 (2024).}

\leavevmode\vadjust pre{\hypertarget{ref-peralta_taxonomy_2008}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{I. E. Peralta, D. M. Spooner, S. Knapp, Taxonomy of wild
tomatoes and their relatives (\emph{solanum} sect.
\emph{Lycopersicoides}, sect. \emph{Juglandifolia}, sect.
\emph{Lycopersicon}; {Solanaceae}). \textbf{84} (2008).}

\leavevmode\vadjust pre{\hypertarget{ref-schoch_dependence_1980}{}}%
\CSLLeftMargin{3. }%
\CSLRightInline{P.-G. Schoch, C. Zinsou, M. Sibi,
\href{https://doi.org/10.1093/jxb/31.5.1211}{Dependence of the stomatal
index on environmental factors during stomatal differentiation in leaves
of \emph{{Vigna} sinensis} {L}.: 1. {Effect} of light intensity}.
\emph{Journal of Experimental Botany} \textbf{31}, 1211--1216 (1980).}

\leavevmode\vadjust pre{\hypertarget{ref-parkhurst_adaptive_1978}{}}%
\CSLLeftMargin{4. }%
\CSLRightInline{D. F. Parkhurst,
\href{https://doi.org/10.2307/2259142}{The adaptive significance of
stomatal occurrence on one or both surfaces of leaves}. \emph{The
Journal of Ecology} \textbf{66}, 367--383 (1978).}

\leavevmode\vadjust pre{\hypertarget{ref-sack_developmental_2016}{}}%
\CSLLeftMargin{5. }%
\CSLRightInline{L. Sack, T. N. Buckley,
\href{https://doi.org/10.1104/pp.16.00476}{The developmental basis of
stomatal density and flux}. \emph{Plant Physiology} \textbf{171},
2358--2363 (2016).}

\leavevmode\vadjust pre{\hypertarget{ref-mott_amphistomy_1991}{}}%
\CSLLeftMargin{6. }%
\CSLRightInline{K. A. Mott, O. Michaelson, Amphistomy as an adaptation
to high light intensity in \emph{{Ambrosia} cordifolia} ({Compositae}).
\emph{American Journal of Botany} \textbf{78}, 76--79 (1991).}

\leavevmode\vadjust pre{\hypertarget{ref-schindelin_fiji_2012}{}}%
\CSLLeftMargin{7. }%
\CSLRightInline{J. Schindelin, I. Arganda-Carreras, E. Frise, V. Kaynig,
M. Longair, T. Pietzsch, S. Preibisch, C. Rueden, S. Saalfeld, B.
Schmid, J.-Y. Tinevez, D. J. White, V. Hartenstein, K. Eliceiri, P.
Tomancak, A. Cardona, \href{https://doi.org/10.1038/nmeth.2019}{Fiji: An
open-source platform for biological-image analysis}. \emph{Nature
Methods} \textbf{9}, 676--682 (2012).}

\leavevmode\vadjust pre{\hypertarget{ref-gelman_inference_1992}{}}%
\CSLLeftMargin{8. }%
\CSLRightInline{A. Gelman, D. B. Rubin, Inference from iterative
simulation using multiple sequences. \emph{Statistical Science}
\textbf{7}, 457--472 (1992).}

\leavevmode\vadjust pre{\hypertarget{ref-burkner_brms_2017}{}}%
\CSLLeftMargin{9. }%
\CSLRightInline{P.-C. Bürkner,
\href{https://doi.org/10.18637/jss.v080.i01}{\textbf{Brms} : {An}
\emph{r} {Package} for {Bayesian} {Multilevel} {Models} {Using}
\emph{stan}}. \emph{Journal of Statistical Software} \textbf{80}
(2017).}

\leavevmode\vadjust pre{\hypertarget{ref-stan_development_team_stan_2023}{}}%
\CSLLeftMargin{10. }%
\CSLRightInline{Stan Development Team, \emph{Stan {Modeling} {Language}
{Users} {Guide} and {Reference} {Manual}} (2023;
\url{https://mc-stan.org}).}

\leavevmode\vadjust pre{\hypertarget{ref-gabry_cmdstanr_2023}{}}%
\CSLLeftMargin{11. }%
\CSLRightInline{J. Gabry, R. Češnovar, \emph{Cmdstanr: {R} {Interface}
to '{CmdStan}'} (2023;
\href{https://mc-stan.org/cmdstanr,\%20https://discourse.mc-stan.org}{https://mc-stan.org/cmdstanr,
https://discourse.mc-stan.org}).}

\leavevmode\vadjust pre{\hypertarget{ref-r_core_team_r:_2023}{}}%
\CSLLeftMargin{12. }%
\CSLRightInline{R Core Team, \emph{R: {A} {Language} and {Environment}
for {Statistical} {Computing}} (R Foundation for Statistical Computing,
Vienna, Austria, 2023; \url{http://www.R-project.org/}).}
